---
title: "2016 Winter INFO 498F Students"
output: html_document
---

```{r message = FALSE, echo = FALSE, warning = FALSE}
# Require these 3 libraries
library(plotly)
library(knitr)
library(dplyr)

# Set the directory.
# setwd("/Users/chasekaylee/Desktop/info498f/a7-collaborative-coding")

# Import the 3 scripts.
source("scripts/Summary_Function.R")
source("scripts/chart_file_1.R")
source("scripts/chart_file_2.R")

# Reads in the info
data <- read.csv("https://raw.githubusercontent.com/INFO-498F/a7-survey-data/master/intro_survey_data.csv")

# Summarizes the data using the summarry_function script
data_info <- sum_func(data)
```

```{r, echo = FALSE,  message = FALSE, warning = FALSE }
total <- sum(data_info$`Students in Class`)

# This function finds the percentage for the following information.
percentOf <- function(x) {
  return(round(x/total * 100))
}

applying <- percentOf(sum(data_info$`Number Applying to Info`))
freshman <- percentOf(data_info$`Students in Class`[1])
sophomores <- percentOf(data_info$`Students in Class`[2])
juniors <- percentOf(data_info$`Students in Class`[3])
seniors <- percentOf(data_info$`Students in Class`[4])
 
mac <- percentOf(data_info$`Number of Users`[3])
windows <- percentOf(data_info$`Number of Users`[2])

cat <- percentOf(data_info$`Number of Pet People`[1])
dog <- percentOf(data_info$`Number of Pet People`[3])
both <- percentOf(data_info$`Number of Pet People`[4])

```
****

## Survey Facts

**`r total`** students of the Winter 2016 Info 498F class took a brief survey. Here are some facts:

- `r applying`% of the students are going to apply to Informatics
- `r freshman`% are freshman
- `r sophomores`% are sophomores
- `r juniors`% are juniors
- `r seniors`% are seniors

- `r mac`% are mac users
- `r windows` % are windows users

- `r cat`% are cat people
- `r dog`% are dog people
- `r both`% are both!


```{r, echo = FALSE, message = FALSE}
# Creates visualization that compares how many of the people in each class standing are planning on  #applying to the Informatics major to the number of people in each class standing.
chart1 <- make_visualization(data)
```

```{r, echo = FALSE, message = FALSE}

# Creates a visualization that compares the countries visited based on what type of operation system the student uses
chart2 <- build_chart(data)
```

This visualization compares how many students in each class standing are planning on  #applying to the Informatics major to the total number of people in each class standing.
`r chart1`


This visualization compares the students' prefered pet based on what type of operation system the student uses
`r chart2`
